### 2019-07-28 paper/paper.tex
Some tidying on the details of the parameter/constraints.

\documentclass{icsc}

\usepackage{siunitx}

@@

\begin{center}
  \fontsize{14}{20}{\bf Optimal bicycle design to maximize handling and safety}
\end{center}

@@

\begin{keywords}
  bicycle,
  design,
  handling qualities,
  control,
  optimization
\end{keywords}

@@

There are six free parameters associated with the rear frame's inertial characteristics:

\begin{description}
  \item[$m_D$] Mass of the rear frame.
  \item[$k_{Dxx}$] Central radius of gyration with respect to the $X$ axis where $k_{Dxx}^2=I_{Dxx} / m_D$.
  \item[$k_{Dyy}$] Central radius of gyration with respect to the $Y$ axis where $k_{Dyy}^2=I_{Dyy} / m_D$.
  \item[$k_{Dzz}$] Central radius of gyration with respect to the $Z$ axis where $k_{Dzz}^2=I_{Dzz} / m_D$.
  \item[$\alpha_D$] Angle between the $X$ axis and the primary principal inertia axis.
  \item[$x_D$] Location along the $X$ axis of the rear frame center of mass.
  \item[$z_D$] Location along the $Z$ axis of the rear frame center of mass.
\end{description}

@@

We assume that the person's joint configurations are such that they are in a nominal configuration for pedaling, i.e. an average normal everyday ???or maximum power?? riding position. The person is assumed to be symmetric about the $XZ$ plane. There are four fixed parameters that enforce this assumption:

@@

@@

\begin{align}
  m_T = m_H + m_B + m_F + m_R \leq 25 \si{kg}
\end{align}

@@

\begin{align}
  p = & [m_D, k_{Dxx}, k_{Dzz}, \alpha_D, x_D, z_D, x_P, z_P, \alpha_P, r_R, m_R, r_F, m_H, \\
      & x_H, z_H, k_{Hxx}, k_{Hyy}, k_{Hzz}, \alpha_H, w, c, \lambda]
\end{align}

with these fixed values:

\begin{align}
  I_{Dxy} = I_{Dyz} = 0 \\
  % 
  l_P = ? \si{m}\\
  w_P = ? \si{m} \\
  m_P = 83.5 \si{kg} \\
  y_P = 0 \si{\meter} \\
  I_{Pxx} = 10.98524 \si{\kg\meter^2} \\
  I_{Pyy} = 11.2571 \si{\kg\meter^2}\\
  I_{Pzz} = 2.26922 \si{\kg\meter^2}\\
  I_{Pxy} = I_{Pyz} = 0 \si{\kg\meter^2}\\
  I_{Pxz} = -1.70211 \si{\kg\meter^2}\\
  %
  I_{Bxy} = I_{Byz} = 0 \\
  % 
  I_{Hxy} = I_{Hyz} = 0 \\
  %
  I_{Rxy} = I_{Ryz} = I_{Rxz} = 0 \\
  %
  I_{Fxy} = I_{Fyz} = I_{Fxz} = 0 \\
\end{align}

@@

\begin{align}
  m_R > 0 \\
  m_F > 0 \\
  m_H > 0 \\
  m_D > 0 \\
  r_R > 0 \\
  r_F > 0 \\
  z_H < 0 \\
  z_D < 0 \\
  -\frac{\pi}{2} \leq \alpha_H \leq \frac{\pi}{2} \\
  -\frac{\pi}{2} \leq \alpha_P \leq \frac{\pi}{2} \\
  -\frac{\pi}{2} \leq \alpha_D \leq \frac{\pi}{2} \\
  -\frac{\pi}{2} \leq \lambda \leq \frac{\pi}{2}
\end{align}

with these parameter convertions:

\begin{align}
  I_{Dxx} = m_D k_{Dxx}^2 \\
  I_{Dzz} = m_D k_{Dzz}^2 \\
  I_{Dyy} = \sqrt{I_{Dxx}^2 + I_{Dzz}^2} \\
  I_{Dxz} = f(I_{Dxx}, I_{Dzz}, \alpha_D)  \\
  %
  m_B = m_D + m_P \\
  x_B = \frac{m_D x_D + m_P x_P}{m_B} \\
  z_B = \frac{m_D z_D + m_P z_P}{m_B} \\
  I_{Bxx} = f(m_B, I_P, I_D, x_D, z_D, x_P, z_P, x_B, z_B) \\
  I_{Byy} = f(m_B, I_P, I_D, x_D, z_D, x_P, z_P, x_B, z_B) \\
  I_{Bzz} = f(m_B, I_P, I_D, x_D, z_D, x_P, z_P, x_B, z_B) \\
  I_{Bxy} = 0 \\
  I_{Byz} = 0 \\
  I_{Bxz} = f(m_B, I_P, I_D, x_D, z_D, x_P, z_P, x_B, z_B) \\
  % 
  I_{Hxx} = m_H k_{Hxx}^2 \\
  I_{Hzz} = m_H k_{Hzz}^2 \\
  I_{Hyy} = \sqrt{I_{Hxx}^2 + I_{Hzz}^2} \\
  I_{Hxz} = f(I_{Hxx}, I_{Hzz}, \alpha_H)  \\
  %
  I_{Ryy} = m_R r_R^2 \\
  I_{Rxx} = I_{Rzz} = I_{Ryy} / 2 \\
  %
  I_{Fyy} = m_F r_F^2 \\
  I_{Fxx} = I_{Fzz} = I_{Fyy} / 2 \\
  %
  m_T = m_H + m_B + m_F + m_R \\
  x_T = \frac{m_H x_H + m_B x_B + m_F w}{m_T} \\
  z_T = \frac{m_H z_H + m_B z_B + m_F r_F + m_R r_R}{m_T} 
\end{align}

@@

\begin{align}
  I_{Hyy} \leq \sqrt{I_{Hxx}^2 + I_{Hzz}^2} \\
  z_P + l_P / 2 \cos{\alpha_P} & \leq 0 \\
  z_P + w_P / 2 \sin{\alpha_P} & \leq 0 \\
  z_P - l_P / 2 \cos{\alpha_P} & \leq 0 \\
  z_P - w_P / 2 \sin{\alpha_P} & \leq 0 \\
  w > r_F + r_R \\
  m_T \leq 25 \si{kg} \\
  \frac{x_T}{|z_t|} < \frac{1}{4} \\
  \frac{x_T - w}{|z_T|} < -1
\end{align}

>>>>

\documentclass{article}

\usepackage{siunitx}
\usepackage{amsmath}

@@

\begin{center}
  \fontsize{14}{20}{\bf Expanded Optimization for Discovering Optimal Lateral
  Handling Bicycles}
\end{center}

@@

@@

There are 5 free parameters associated with the rear frame's inertial
characteristics:

\begin{description}
  \item[$m_D$] Mass of the rear frame.
  \item[$x_D$] Location along the $X$ axis of the rear frame center of mass.
  \item[$z_D$] Location along the $Z$ axis of the rear frame center of mass.
  \item[$k_{Dxx}$] Central radius of gyration with respect to the $X$ axis
    where $k_{Dxx}^2=I_{Dxx} / m_D$.
  \item[$k_{Dzz}$] Central radius of gyration with respect to the $Z$ axis
    where $k_{Dzz}^2=I_{Dzz} / m_D$.
  \item[$\alpha_D$] Angle between the $X$ axis and the primary principal
    inertia axis.
\end{description}

Assumptions:

@@

We assume that the person's joint configurations are such that they are in a
nominal configuration for pedaling, i.e. an average normal everyday riding
position. The person is assumed to be symmetric about the $XZ$ plane. There are
four fixed parameters that enforce this assumption:

@@

Assumptions:

\begin{itemize}
  \item We allow for any angular orientation of the $XZ$ principal directions
    but limit the angle to $-\frac{\pi}{2} \leq \alpha_H \leq \frac{\pi}{2}$.
\end{itemize}

@@

\begin{align}
  m_T = m_H + m_D + m_P + m_F + m_R \leq m_P + 25 \si{kg}
\end{align}

@@

\begin{align}
  \mathbf{p} =
  \begin{bmatrix}
    % front frame
    m_D \\
    x_D \\
    z_D \\
    k_{Dxx} \\
    k_{Dzz} \\
    \alpha_D \\
    % person
    x_P \\
    z_P \\
    \alpha_P \\
    % front frame
    m_H \\
    x_H \\
    z_H \\
    k_{Hxx} \\
    k_{Hyy} \\
    k_{Hzz} \\
    I_{Hxz} \\
    \alpha_H \\
    % rear wheel
    r_R \\
    m_R \\
    % front wheel
    r_F \\
    m_F \\
    % primary geometry
    w \\
    c \\
    \lambda
  \end{bmatrix}
\end{align}

with these additional parameters that have fixed values:

\begin{align}
  I_{Dxy} = I_{Dyz} = 0 \\
  y_D = 0 \\
  % 
  l_P = ? \si{m}\\
  w_P = ? \si{m} \\
  m_P = 83.5 \si{kg} \\
  y_P = 0 \si{\meter} \\
  I_{Pxx} = 10.98524 \si{\kg\meter^2} \\
  I_{Pyy} = 11.2571 \si{\kg\meter^2}\\
  I_{Pzz} = 2.26922 \si{\kg\meter^2}\\
  I_{Pxy} = I_{Pyz} = 0 \si{\kg\meter^2}\\
  I_{Pxz} = -1.70211 \si{\kg\meter^2}\\
  % 
  I_{Hxy} = I_{Hyz} = 0 \\
  y_H = 0 \\
  %
  I_{Rxy} = I_{Ryz} = I_{Rxz} = 0 \\
  %
  I_{Fxy} = I_{Fyz} = I_{Fxz} = 0 \\
\end{align}

with these conversions from our parameters to the benchmark parameters:

\begin{align}
  I_{Dxx} = m_D k_{Dxx}^2 \\
  I_{Dyy} = \sqrt{I_{Dxx}^2 + I_{Dzz}^2} \\
  I_{Dzz} = m_D k_{Dzz}^2 \\
  I_{Dxz} = f(I_{Dxx}, I_{Dzz}, \alpha_D)  \\
  %
  m_B = m_D + m_P \\
  x_B = \frac{m_D x_D + m_P x_P}{m_B} \\
  z_B = \frac{m_D z_D + m_P z_P}{m_B} \\
  I_{Bxx} = f(m_B, I_P, I_D, x_D, z_D, x_P, z_P, x_B, z_B) \\
  I_{Byy} = f(m_B, I_P, I_D, x_D, z_D, x_P, z_P, x_B, z_B) \\
  I_{Bzz} = f(m_B, I_P, I_D, x_D, z_D, x_P, z_P, x_B, z_B) \\
  I_{Bxy} = 0 \\
  I_{Byz} = 0 \\
  I_{Bxz} = f(m_B, I_P, I_D, x_D, z_D, x_P, z_P, x_B, z_B) \\
  % 
  I_{Hxx} = m_H k_{Hxx}^2 \\
  I_{Hyy} = m_H k_{Hyy}^2\\
  I_{Hzz} = m_H k_{Hzz}^2 \\
  I_{Hxz} = f(I_{Hxx}, I_{Hzz}, \alpha_H)  \\
  %
  I_{Ryy} = m_R r_R^2 \\
  I_{Rxx} = I_{Ryy} / 2 \\
  I_{Rzz} = I_{Ryy} / 2 \\
  %
  I_{Fyy} = m_F r_F^2 \\
  I_{Fxx} = I_{Fyy} / 2 \\
  I_{Fzz} = I_{Fyy} / 2 \\
  %
  m_T = m_H + m_B + m_F + m_R \\
  x_T = \frac{m_H x_H + m_B x_B + m_F w}{m_T} \\
  z_T = \frac{m_H z_H + m_B z_B + m_F r_F + m_R r_R}{m_T} 
\end{align}

@@

\begin{align}
  m_R > 0 \\
  m_F > 0 \\
  m_H > 0 \\
  m_D > 0 \\
  r_R > r_{min} \\
  r_F > r_{min} \\
  z_H < 0 \\
  z_D < 0 \\
  -\frac{\pi}{2} \leq \alpha_H \leq \frac{\pi}{2} \\
  -\frac{\pi}{2} \leq \alpha_P \leq \frac{\pi}{2} \\
  -\frac{\pi}{2} \leq \alpha_D \leq \frac{\pi}{2} \\
  -\frac{\pi}{2} \leq \lambda \leq \frac{\pi}{2}
\end{align}

@@

\begin{align}
  I_{Hyy} \leq \sqrt{I_{Hxx}^2 + I_{Hzz}^2} \\
  z_P + l_P / 2 \cos{\alpha_P} & \leq 0 \\
  z_P + w_P / 2 \sin{\alpha_P} & \leq 0 \\
  z_P - l_P / 2 \cos{\alpha_P} & \leq 0 \\
  z_P - w_P / 2 \sin{\alpha_P} & \leq 0 \\
  w > r_F + r_R \\
  m_{Tmin} + m_P \leq m_T \leq 25 \si{kg} + m_P \\
  \frac{x_T}{|z_T|} < \frac{1}{4} \\
  \frac{x_T - w}{|z_T|} < -1 \\
  real(\mathbf{s}) < 0
\end{align}
